Temperature Measurements in Optical Tweezer Experiments

### 2017-01-18 doc/draft1.tex
updates

\subsection{Barostat}
The barostat, as described in the previous section, keeps the system from overheating. The algorithm is applied at the same time as the eHEX algorithm
which leads to the fact, that the system has time to heat up, until the particles reach the nano crystal. This can be seen in the temperature
development in fig.~\ref{fig:baro1}.
\begin{figure}[h]
    \begin{center}
        \includegraphics[scale=0.4]{images/ehex_te.pdf}
        \caption{}
        \label{fig:baro1}
    \end{center}
\end{figure}

>>>>

\subsection{Barostat}
The barostat, as described previously, keeps the system from overheating. The barostat algorithm is applied at the same time as the eHEX algorithm,
after the velocity Verlet has equilibrated the system.\\
While the eHEX algorithm is pumping energy into the nano crystal while the surrounding gas particles absorb excessive energy. This leads to the
development of a new, higher steady temperature of the nano crystal, which can be seen in fig.~\ref{fig:baro1}. The first simulations were performed
with the eHEX and the barostat algorithm starting at the same point. This lead to the question: does the new steady temperature depend on the time it
takes the gas particles to reach the system? The answer is: no. After applying the barostat algorithm first to fill the box with gas atoms and then
applying the eHEX algorithm it can be seen that the resulting temperature is the same, which can be seen in fig.~\ref{fig:baro2}.
%This means that the system is beginning to heat up, until the particles reach the crystal.
%Because of this, the temperature of the system rises, until it reaches a steady value again. This behaviour can be seen in fig.~\ref{fig:baro1}.\\
        \includegraphics[scale=0.4]{images/baro_temp_start.pdf}
        \caption{Temperature of the system during the application of the eHEX and the barostat algorithm. During the first 20000 steps the system is
        in equilibrium while the velocity Verlet algorithm is applied. After that, the eHEX and the barostat algorithms are turned on. This leads to
    an increase in temperature until a new steady temperature is reached.}
        %\caption{Temperature of the system during the application of the eHEX and the barostat algorithm. During the first 20000 steps the system is
        %in equilibrium while the velocity Verlet algorithm is applied. After that, the eHEX and the barostat algorithms are turned on. This leads to
    %an increase in temperature until the gas particles reach the nano crystal to slow down the heating of the system. After some time, a plateau is
%reached and the temperature seems to stay at this value.}
        \label{fig:baro1}
        \includegraphics[scale=0.4]{images/baro_temp_compare_other.pdf}
        \caption{Two versions of the application of the eEHX and barostat algorithm. The shorter run (red, x-axis on the bottom) represents 
            the simultaneous start of the eHEX and the barostat algorithm. In the longer run (blue, x-axis on the top) there are 20000 steps, where
        the barostat algorithm is applied at the same time as the velocity Verlet to give the system time to equilibrate and only after the eHEX
    algorithm is taking the place of the velocity Verlet. The mean value of the resulting temperature is the same, indicating that the final
temperature is based on the values of the parameters, such as pressure and ambient temperature, rather than geometry.}
        %\caption{Temperature of the system during the application of the eHEX and the barostat algorithm. During the first 20000 steps the system is
        %in equilibrium while the velocity Verlet algorithm is applied. After that, the eHEX and the barostat algorithms are turned on. This leads to
    %an increase in temperature until the gas particles reach the nano crystal to slow down the heating of the system. After some time, a plateau is
%reached and the temperature seems to stay at this value.}
        \label{fig:baro1}
As we are interested in the temperatures of the particles before and after the interaction with the crystal, we need some way to differentiate those
two states. This can be done when looking at the total energy of the gas particles.\\
The gas particles are created on the surface of the simulation box, which is further away than the interaction range between the gas particles and the
nano crystal. Since the gas particles do not interact with each other, the total energy of the gas particles does not change until they reach the
interaction range of the nano crystal. There they undergo a change of energy due to the interaction with the nano crystal and then make their way away
from the nano crystal. After the interaction, when they reach a point outside of the interaction range, the enrgy stays constant again until the
particles reach the limits of the simulation box.\\
Therefore, the life span of a single gas particle can be partioned into 3 stages: incoming, interacting, outgoing. In a typical scene of interaction
all three of these stages are represented by different gas particles, as can be seen in fig.~\ref{fig:barointeraction}.\\
        \includegraphics[scale=0.4]{images/baro_170105_new_medium.png}
        \caption{Rendering of the application of the barostat algorithm. The red particles are incoming gas particles, that have not yet interacted, 
            pink particles are currently interacting and green particles are leaving the simulation box and
        moving away from the nano crystal (blue). To render this image, a cut has been made to make a view into the simulation box possible.}
        \label{fig:barointeraction}
Since the gas particles are interacting with the nano crystal, the temperatures and energies are values of interest. The energies are recorded using
histograms and the temperature is calculated instantaneously every 100th timestep.\\
The calculation of the energies of the incoming particles has to be done with care. The problem are particles that enter the simulation box, but fly
by the nano crystal at a distance that is greater than the interaction range. Since the change of the energy is the interesting part, only the energy 
particles of that \textit{do} interact with the nano crystal shall be calculated. This can be achieved by counting particles that enter the stage of
\textit{interacing}
